Appendix 1.F: Analysing global trends in within-country inequality

### 2023-01-29 PhD_pages/data_appendices/1_F_within_country_trends.qmd
Paper 1, more conversion to python

---
title: "Appendix 1.B: Analysing global trends in within-country inequality"
format: html
warning: false
filters:
  - shinylive

@@

```{python}
#  ---------------------------------
#  ---------- SECTION 2: Specifications -------------
#  ----------------------------------

@@

This second block of code we read in the data (this needs to be done in a different way in )

#  ---------------------------------
#  ---------- SECTION 3: Read in data -------------
#  ----------------------------------

url = 'https://raw.githubusercontent.com/JoeHasell/personal_site/main/PhD_pages/data_appendices/data/clean/WID_region_mapping.csv'

@@

```{shinylive-python}
#| standalone: true
#| viewerHeight: 420

from shiny import *
from plotnine import *
from pyodide.http import open_url
import pandas as pd
import numpy as np

#  ---------------------------------
#  ---------- Data prep functions -------------
#  ----------------------------------

#  ---------------------------------
#  ---------- Specifications -------------
#  ----------------------------------

source_count_requirement = 2

#  ---------------------------------
#  ---------- App code -------------
#  ----------------------------------

def panel_box(*args, **kwargs):
    return ui.div(
        ui.div(*args, class_="card-body"),
        **kwargs,
        class_="card mb-3",
    )

app_ui = ui.page_fluid(
    {"class": "p-4"},
    ui.row(
        ui.column(
            4,
            panel_box(
                ui.input_slider("reference_vals", "Reference years", 1975, 2020, value=[1990,2018]),
                ui.input_numeric(
                            "max_dist_from_refs",
                            "=/- (years)",
                            4,
                        ),
                ui.input_numeric(
                            "min_dist_between",
                            "Min distance between observations (years)",
                            23,
                        ),
                ui.input_action_button(
                    "download", "Download data and image", class_="btn-primary w-100"
                ),
            ),
            ui.navset_tab_card(
                ui.nav(
                    "Compare sources",
                    ui.input_select(
                "metric",
                "Metric",
                {
                    "Gini": "Gini",
                    "Top_10_share": "Top 10p.c. share",
                },
            ),
            ),
                ui.nav(
                  "Compare metrics"),
            ),
        ),
        ui.column(
            8,
            ui.output_plot("example_plot")
            ),
    ),
)

def server(input, output, session):
    @output
    @render.plot
    def example_plot():

      df_pip = pd.read_csv(open_url(url))

      df_wid = pd.read_csv(open_url(url))

      url = 'https://raw.githubusercontent.com/JoeHasell/personal_site/main/PhD_pages/data_appendices/data/clean/WID_region_mapping.csv'

      df_regions = pd.read_csv(open_url(url))

      df_pop = pd.read_csv(open_url(url))

      def prep_wid_pip_data(reference_vals, max_dist_from_refs, min_dist_between, reference_col, group_by_col, value_col):

        pip_matches = pip_welfare_routine(
          df = df_pip,
          reference_vals = reference_vals,
          max_dist_from_refs = max_dist_from_refs,
          min_dist_between = min_dist_between,
          reference_col = reference_col,
          group_by_col = group_by_col,
          value_col = value_col
        )

        wid_matches = merge_two_ref_matches(
          df = df_wid,
          reference_vals = reference_vals,
          max_dist_from_refs = max_dist_from_refs,
          min_dist_between = min_dist_between,
          reference_col = reference_col,
          group_by_col = group_by_col,
          value_col = value_col
        )

        ref_pairs = pd.concat([pip_matches, wid_matches,], keys=['pip', 'wid'])

        # Tidy up indexes
        ref_pairs = ref_pairs.reset_index()

        ref_pairs = ref_pairs.drop('level_1', axis=1)

        ref_pairs = ref_pairs\
          .rename(columns={"level_0": "source"})

        return ref_pairs

      def prep_plot_and_tables(
        reference_vals, 
        max_dist_from_refs,
        min_dist_between,
        reference_col,
        group_by_col,
        value_col,
        tolerance,
        outlier_cut_off_upper,
        source_count_requirement):

        plot_data = prep_wid_pip_data(
          reference_vals = reference_vals, 
          max_dist_from_refs = max_dist_from_refs,
          min_dist_between = min_dist_between,
          reference_col = reference_col,
          group_by_col = group_by_col,
          value_col = value_col,
        )

        # Store the names of the columns to be used onthe X and Y axis
        x_axis = f'{value_col}{reference_vals[0]}'
        y_axis = f'{value_col}{reference_vals[1]}'

        # Add a count by country – showing whether data is available from both sources or not
        plot_data['source_count'] = plot_data.groupby(group_by_col)['source'].transform('count')

        # Apply source requirement (whether to include only observations with data from both sources)
        plot_data = plot_data.loc[plot_data['source_count'] >= source_count_requirement]

        plot = (ggplot(plot_data
        , aes(x_axis, y_axis, alpha=0.5))
        + geom_point(aes(color=region_col, size='avg_pop', alpha = 0.6))
        + facet_wrap('~ source')
        + geom_polygon(aes(x='x', y='y', alpha = 0.2), data=shaded_coord)
        + theme_light()
        + theme(legend_position='none')
        )

        group_yes_vars = ['source', region_col]
        group_no_vars = ['source']

          agg_level['global_pop_weights'] = agg_level.groupby('source')['avg_pop'].transform(lambda x: x/x.sum())

      plot_and_tables = prep_plot_and_tables(
          reference_vals = list(input.reference_vals()), 
          max_dist_from_refs = input.max_dist_from_refs(),
          min_dist_between = input.min_dist_between(),
          reference_col = reference_col,
          group_by_col = group_by_col,
          value_col = input.metric(),
          tolerance = tolerance,
          outlier_cut_off_upper = outlier_cut_off_upper,
          source_count_requirement = source_count_requirement
          )

      plot = plot_and_tables['plot']

      return plot

app = App(app_ui, server)

>>>>

---
title: "Appendix 1.F: Analysing global trends in within-country inequality"
format: html
warning: false
filters:
  - shinylive

@@

This second block of code we read in the data (this needs to be done in a different way in the shiny app...)

#  ---------------------------------
#  ---------- SECTION 2: Read in data -------------
#  ----------------------------------

url = 'https://raw.githubusercontent.com/JoeHasell/personal_site/main/PhD_pages/data_appendices/data/clean/region_mapping.csv'

In a third block, we set specifications for the data matching. This is different in the app because some parameters are controlled by the app.

```{python}
#  ---------------------------------
#  ---------- SECTION 3: Specifications -------------
#  ----------------------------------

@@

In this code block we run the code and prepare final plots and tables.

@@

```{shinylive-python}
# #| standalone: true
# #| viewerHeight: 420

# from shiny import *
# from plotnine import *
# from pyodide.http import open_url
# import pandas as pd
# import numpy as np

# #  ---------------------------------
# #  ---------- Data prep functions -------------
# #  ----------------------------------

# #  Function get matching for ref years
# def closest_to_reference(df, reference_val, max_dist_from_ref, reference_col, group_by_col, value_col, tie_break):

#   df = df.loc[:, [reference_col, group_by_col, value_col]]

#   # Drop NAs
#   df = df.dropna()

#   # Calculate absolute distance from reference value
#   df['ref_diff'] = abs(df[reference_col] - reference_val)

#   # Drop any rows with a distance beyond threshold
#   if not pd.isna(max_dist_from_ref):
#     df = df.loc[df['ref_diff'] <= max_dist_from_ref]

#   # Keep closest observation to reference value – including tie-breaks (where there is a match above and below the ref value)
#   df = df[df.groupby(group_by_col)['ref_diff'].transform('min') == df['ref_diff']].reset_index(drop=True)

#   # Settle tie-breaks
#   if tie_break == 'below':
#     df = df[df.groupby(group_by_col)[reference_col].transform('min') == df[reference_col]].reset_index(drop=True)

#   elif tie_break == 'above':
#     df = df[df.groupby(group_by_col)[reference_col].transform('max') == df[reference_col]].reset_index(drop=True)

#   df = df.drop('ref_diff', axis=1)

#   return df

# # Merge matches for different reference points
# def merge_two_ref_matches(df, reference_vals, max_dist_from_refs, min_dist_between, reference_col, group_by_col, value_col):

# # Make sure the pair of reference values are in ascending order
#   reference_vals.sort()

# # Maximise distance between two refs by settling tie-breaks below the lowest ref and above the highest ref

# # Find matches for lower reference value
#   lower_ref_matches = closest_to_reference(df, reference_vals[0], max_dist_from_refs, reference_col, group_by_col, value_col, 'below')

# # Find matches for higher reference value
#   higher_ref_matches = closest_to_reference(df, reference_vals[1], max_dist_from_refs, reference_col, group_by_col, value_col, 'above')

# # Merge the two sets of matches
#   merged_df = pd.merge(lower_ref_matches, higher_ref_matches, on=group_by_col, suffixes=(reference_vals[0], reference_vals[1]))

# # Drop obs that do not have data for both ref values
#   merged_df = merged_df.dropna()

# # Drop obs where the matched data does not meet the min distance requirement
#   if not pd.isna(min_dist_between):

#   # Store the names of the reference column returned from the two matches
#     ref_var_high = f'{reference_col}{reference_vals[1]}'
#     ref_var_low = f'{reference_col}{reference_vals[0]}'

#   # Keep only rows >= to the min distance
#     merged_df = merged_df.loc[(merged_df[ref_var_high] - merged_df[ref_var_low]) >= min_dist_between, :]

#   return merged_df

#   # For PIP run this three times – first filtering data for just consumpion only, then with income only, then with a dataset that prefers income over consumption
# def pip_welfare_routine(df, reference_vals, max_dist_from_refs, min_dist_between, reference_col, group_by_col, value_col):

#     # Specify the name of the column in which the income/consumption welfare definition is stored
#     welfare_colname = 'welfare_type'

#     # Creat dataframes for thee scenarios:
#     # Scenario 1: only allow income data
#     df_inc_filter = df.loc[df[welfare_colname] == "income", :]
#     df_inc_filter.name = "Income"

#     # Scenario 2: only allow consumption data
#     df_cons_filter = df.loc[df[welfare_colname] == "consumption", :]
#     df_cons_filter.name = "Consumption"
#     # Scenario 3: allow a mix – dropping consumption data where income data is available in the same year
#     df_mixed = df.copy()

#     df_mixed['welfare_count'] = df_mixed.groupby([reference_col, group_by_col])[welfare_colname].transform('count')

#     df_mixed = df_mixed.loc[(df_mixed['welfare_count'] == 1) | (df_mixed[welfare_colname] == "income")]

#     df_mixed.name = "Mixed"
#     #  Store the scneario dataframes in a list
#     df_scenarios = [df_inc_filter, df_cons_filter, df_mixed]

#     # Run the matching function on each scenario
#     scenario_matches = [merge_two_ref_matches(
#       df_scenario, 
#       reference_vals, 
#       max_dist_from_refs, 
#       min_dist_between, 
#       reference_col, 
#       group_by_col, 
#       value_col) for df_scenario in df_scenarios]

#     # Combine the first two scenarios.
#     df_combined_matches = pd.concat([scenario_matches[0], scenario_matches[1]], keys=[df_scenarios[0].name, df_scenarios[1].name])

#     # Tidy up indexes
#     df_combined_matches = df_combined_matches.reset_index()

#     df_combined_matches = df_combined_matches.drop('level_1', axis=1)

#     df_combined_matches = df_combined_matches\
#       .rename(columns={"level_0": "pip_welfare"})

#     # Add in third scenario.
#     df_combined_matches = pd.concat([df_combined_matches, scenario_matches[2]])

#     # add scenario name to te pip_welfare column
#     df_combined_matches['pip_welfare'] = df_combined_matches['pip_welfare'].fillna(df_scenarios[2].name)

#     # Keep only one match per group (e.g. per Country) - in the priority laid out in the df_scenarios list above (income only -> consumption only -> mixed)
#       # First count the matches
#     df_combined_matches['match_count'] = df_combined_matches.groupby(group_by_col)['pip_welfare'].transform('count')
#       # Then drop any matches from the lowest priority where there are multiple matches
#     df_combined_matches = df_combined_matches.loc[(df_combined_matches['match_count']==1) | ~(df_combined_matches['pip_welfare']==df_scenarios[2].name)]
#       #  Repeat at the next level of priority
#     df_combined_matches['match_count'] = df_combined_matches.groupby(group_by_col)['pip_welfare'].transform('count')
#     df_combined_matches = df_combined_matches.loc[(df_combined_matches['match_count']==1) | ~(df_combined_matches['pip_welfare']==df_scenarios[1].name)]

#     # Drop the match count column
#     df_combined_matches = df_combined_matches.drop('match_count', axis=1)

#     return df_combined_matches

# #  ---------------------------------
# #  ---------- Specifications -------------
# #  ----------------------------------

# # These parameters are not controlled in the app.
# reference_col = 'Year'
# group_by_col = 'Entity'

# tolerance = 1
# outlier_cut_off_upper = None

# source_count_requirement = 2

# #  ---------------------------------
# #  ---------- App code -------------
# #  ----------------------------------

# def panel_box(*args, **kwargs):
#     return ui.div(
#         ui.div(*args, class_="card-body"),
#         **kwargs,
#         class_="card mb-3",
#     )

# app_ui = ui.page_fluid(
#     {"class": "p-4"},
#     ui.row(
#         ui.column(
#             4,
#             panel_box(
#                 ui.input_slider("reference_vals", "Reference years", 1975, 2020, value=[1990,2018]),
#                 ui.input_numeric(
#                             "max_dist_from_refs",
#                             "=/- (years)",
#                             4,
#                         ),
#                 ui.input_numeric(
#                             "min_dist_between",
#                             "Min distance between observations (years)",
#                             23,
#                         ),
#                 ui.input_action_button(
#                     "download", "Download data and image", class_="btn-primary w-100"
#                 ),
#             ),
#             ui.navset_tab_card(
#                 ui.nav(
#                     "Compare sources",
#                     ui.input_select(
#                 "metric",
#                 "Metric",
#                 {
#                     "Gini": "Gini",
#                     "Top_10_share": "Top 10p.c. share",
#                 },
#             ),
#             ),
#                 ui.nav(
#                   "Compare metrics"),
#             ),
#         ),
#         ui.column(
#             8,
#             ui.output_plot("example_plot")
#             ),
#     ),
# )

# def server(input, output, session):
#     @output
#     @render.plot
#     def example_plot():

#       url = 'https://raw.githubusercontent.com/JoeHasell/personal_site/main/PhD_pages/data_appendices/data/clean/pip.csv'

#       df_pip = pd.read_csv(open_url(url))

#       url = 'https://raw.githubusercontent.com/JoeHasell/personal_site/main/PhD_pages/data_appendices/data/clean/wid.csv'

#       df_wid = pd.read_csv(open_url(url))

#       url = 'https://raw.githubusercontent.com/JoeHasell/personal_site/main/PhD_pages/data_appendices/data/clean/region_mapping.csv'

#       df_regions = pd.read_csv(open_url(url))

#       url = 'https://raw.githubusercontent.com/JoeHasell/personal_site/main/PhD_pages/data_appendices/data/clean/population.csv'

#       df_pop = pd.read_csv(open_url(url))

#       def prep_wid_pip_data(reference_vals, max_dist_from_refs, min_dist_between, reference_col, group_by_col, value_col):

#         pip_matches = pip_welfare_routine(
#           df = df_pip,
#           reference_vals = reference_vals,
#           max_dist_from_refs = max_dist_from_refs,
#           min_dist_between = min_dist_between,
#           reference_col = reference_col,
#           group_by_col = group_by_col,
#           value_col = value_col
#         )

#         wid_matches = merge_two_ref_matches(
#           df = df_wid,
#           reference_vals = reference_vals,
#           max_dist_from_refs = max_dist_from_refs,
#           min_dist_between = min_dist_between,
#           reference_col = reference_col,
#           group_by_col = group_by_col,
#           value_col = value_col
#         )

#         ref_pairs = pd.concat([pip_matches, wid_matches,], keys=['pip', 'wid'])

#         # Tidy up indexes
#         ref_pairs = ref_pairs.reset_index()

#         ref_pairs = ref_pairs.drop('level_1', axis=1)

#         ref_pairs = ref_pairs\
#           .rename(columns={"level_0": "source"})

#         return ref_pairs

#       def prep_plot_and_tables(
#         reference_vals, 
#         max_dist_from_refs,
#         min_dist_between,
#         reference_col,
#         group_by_col,
#         value_col,
#         tolerance,
#         outlier_cut_off_upper,
#         source_count_requirement):

#         # Other spec:
#         region_col = 'region_alt'

#         # ---- Prep data ---------

#         plot_data = prep_wid_pip_data(
#           reference_vals = reference_vals, 
#           max_dist_from_refs = max_dist_from_refs,
#           min_dist_between = min_dist_between,
#           reference_col = reference_col,
#           group_by_col = group_by_col,
#           value_col = value_col,
#         )

#         # Store the names of the columns to be used onthe X and Y axis
#         x_axis = f'{value_col}{reference_vals[0]}'
#         y_axis = f'{value_col}{reference_vals[1]}'

#         x_ref_val = f'{reference_col}{reference_vals[0]}'
#         y_ref_val = f'{reference_col}{reference_vals[1]}'

#         # Apply outlier cut off, if specified
#         if not pd.isna(outlier_cut_off_upper):
#           plot_data = plot_data.loc[plot_data[x_axis] <= outlier_cut_off_upper]
#           plot_data = plot_data.loc[plot_data[y_axis] <= outlier_cut_off_upper]

#         # Add a count by country – showing whether data is available from both sources or not
#         plot_data['source_count'] = plot_data.groupby(group_by_col)['source'].transform('count')

#         # Apply source requirement (whether to include only observations with data from both sources)
#         plot_data = plot_data.loc[plot_data['source_count'] >= source_count_requirement]

#         # Drop source_count column
#         plot_data = plot_data.drop('source_count', axis=1)

#         # Add in region classification
#         plot_data = pd.merge(plot_data, df_regions, how = 'left')

#         # Add in population data
#           # For first ref
#         df_pop_ref = df_pop.loc[df_pop['Year'] == reference_vals[0], ['Entity', 'population'] ]

#         plot_data = pd.merge(plot_data, df_pop_ref, how = 'left')

#         plot_data = plot_data.rename(columns={'population':'population_ref1'})

#           # For second ref
#         df_pop_ref = df_pop.loc[df_pop['Year'] == reference_vals[1], ['Entity', 'population'] ]

#         plot_data = pd.merge(plot_data, df_pop_ref, how = 'left')

#         plot_data = plot_data.rename(columns={'population':'population_ref2'})

#           # Calculate average population two reference periods
#         plot_data['avg_pop'] = (plot_data['population_ref1'] + plot_data['population_ref2'])/2

#         # ----- Prep plot ------

#         # I grab what I am guessing to be the max and min tick marks on the x axist, in order to define the coordinates of a 'tolerance' ribbon.
#         x_min = plot_data[x_axis].min()
#         x_min_floor = np.floor(x_min * 10) / 10

#         x_max = plot_data[x_axis].max()
#         x_max_ceiling = np.ceil(x_max * 10) / 10

#         # Set the coordinates of the shaded ribbon
#         shaded_coord = pd.DataFrame({'x': [x_min_floor, x_max_ceiling, x_max_ceiling, x_min_floor], 
#           'y': [x_min_floor-tolerance, x_max_ceiling-tolerance, x_max_ceiling+tolerance , x_min_floor+tolerance]})

#         plot = (ggplot(plot_data
#         , aes(x_axis, y_axis, alpha=0.5))
#         + geom_point(aes(color=region_col, size='avg_pop', alpha = 0.6))
#         + facet_wrap('~ source')
#         + geom_polygon(aes(x='x', y='y', alpha = 0.2), data=shaded_coord)
#         + theme_light()
#         + theme(legend_position='none')
#         )

#         # ---- Prep summary table ----

#         # Calculate the change between the two ref periods
#         plot_data['change'] = (plot_data[y_axis] - plot_data[x_axis])

#         group_yes_vars = ['source', region_col]
#         group_no_vars = ['source']

#         group_scenarios = [group_no_vars, group_yes_vars]

#         aggs = []

#         for group_vars in group_scenarios:

#         # Prepare pop-weighted average change
#           agg_level = plot_data.copy()

#           # Calulate pop weights by source and region
#           agg_level['regional_pop_weights'] = agg_level.groupby(group_vars)['avg_pop'].transform(lambda x: x/x.sum())

#           agg_level['global_pop_weights'] = agg_level.groupby('source')['avg_pop'].transform(lambda x: x/x.sum())

#           # Multiply the change by the pop weights 
#           agg_level['region_weighted_change'] = agg_level['change'] * agg_level['regional_pop_weights']

#         # Prepare fall/stable/rise categories
#           agg_level['fall'] = agg_level['change'] < -tolerance

#           agg_level['stable'] = (agg_level['change'] <= tolerance) & (agg_level['change'] >= -tolerance)

#           agg_level['rise'] = agg_level['change'] > tolerance

#           agg_level[['fall', 'stable', 'rise']] = agg_level[['fall', 'stable', 'rise']].astype(int)

#           agg_level = agg_level.groupby(group_vars)[['change', 'region_weighted_change', 'global_pop_weights', 'fall', 'stable', 'rise']]\
#             .agg(['sum', 'mean', 'count'])

#         # Aggregate by source and region
#           if group_vars == group_yes_vars:

#             agg_level = agg_level\
#               .unstack().T.reset_index()

#           elif group_vars == group_no_vars:

#             agg_level = agg_level\
#               .T.reset_index()

#             agg_level[region_col] = "World"

#           aggs.append(agg_level)

#         df_summary = pd.concat(aggs)

#           # filter for the aggregations we need and label in the 'summary' column
#         df_summary.loc[(df_summary['level_0'] == 'change') & (df_summary['level_1'] == 'mean'), 'summary'] = 'avg change'

#         df_summary.loc[(df_summary['level_0'] == 'region_weighted_change') & (df_summary['level_1'] == 'sum'), 'summary'] = 'Regional pop-weighted avg change'

#         df_summary.loc[(df_summary['level_0'] == 'global_pop_weights') & (df_summary['level_1'] == 'sum'), 'summary'] = 'Global pop weights'

#         df_summary.loc[(df_summary['level_0'] == 'change') & (df_summary['level_1'] == 'count'), 'summary'] = 'n'

#         df_summary.loc[(df_summary['level_0'] == 'fall') & (df_summary['level_1'] == 'sum'), 'summary'] = 'fall'

#         df_summary.loc[(df_summary['level_0'] == 'stable') & (df_summary['level_1'] == 'sum'), 'summary'] = 'stable'

#         df_summary.loc[(df_summary['level_0'] == 'rise') & (df_summary['level_1'] == 'sum'), 'summary'] = 'rise'

#         df_summary = df_summary[df_summary['summary'].notnull()]

#         df_summary = df_summary.drop(['level_0', 'level_1'], axis = 1)

#         df_summary['summary'] = pd.Categorical(df_summary['summary'], categories=['fall', 'stable', 'rise','n', 'avg change', 'Regional pop-weighted avg change', 'Global pop weights'], ordered=True)

#         df_summary = df_summary.sort_values([region_col,'summary']).set_index([region_col,'summary'])

#         # format to show appropriate d.p. I run a loop over each row for want of figuring out a better way!
#         repeat_length = 7
#         for i in range(0, len(df_summary.index.levels[0].unique())):
#           df_summary.iloc[i*repeat_length,:] = df_summary.iloc[i*repeat_length,:].map('{:.0f}'.format)
#           df_summary.iloc[1 + i*repeat_length,:] = df_summary.iloc[1 + i*repeat_length,:].map('{:.0f}'.format)
#           df_summary.iloc[2 + i*repeat_length,:] = df_summary.iloc[2 + i*repeat_length,:].map('{:.0f}'.format)
#           df_summary.iloc[3 + i*repeat_length,:] = df_summary.iloc[3 + i*repeat_length,:].map('{:.0f}'.format)
#           df_summary.iloc[4 + i*repeat_length,:] = df_summary.iloc[4 + i*repeat_length,:].map('{:.2f}'.format)
#           df_summary.iloc[5 + i*repeat_length,:] = df_summary.iloc[5 + i*repeat_length,:].map('{:.2f}'.format)
#           df_summary.iloc[6 + i*repeat_length,:] = df_summary.iloc[6 + i*repeat_length,:].map('{:.2f}'.format)

#         # ----- Return outputs ------
#         plot_and_tables = {
#           "table_data": plot_data,
#           "plot": plot,
#           "summary": df_summary
#         }

#         return plot_and_tables

#       plot_and_tables = prep_plot_and_tables(
#           reference_vals = list(input.reference_vals()), 
#           max_dist_from_refs = input.max_dist_from_refs(),
#           min_dist_between = input.min_dist_between(),
#           reference_col = reference_col,
#           group_by_col = group_by_col,
#           value_col = input.metric(),
#           tolerance = tolerance,
#           outlier_cut_off_upper = outlier_cut_off_upper,
#           source_count_requirement = source_count_requirement
#           )

#       plot = plot_and_tables['plot']

#       return plot

# app = App(app_ui, server)
